% !TeX root = ../main.tex

% Acknowledgements are the author's statement of gratitude to and
% recognition of the people and institutions who helped the author's
% research and writing.

\pretocheader{\bfseries\MakeTextUppercase{Acknowledgements}}

There are many people I would like to extend my gratitude towards throughout the duration of my time here at UNC. First, I would like to thank my advisor, Dr. Harvey Seim, for giving me this opportunity to carry out this honors thesis work. I was given the opportunity to carry out undergraduate research with Dr. Seim during my first year of university, and ever since, I have not taken my foot off the pedal. Dr. Seim introduced me to the turbulent world of physical oceanography, and has inspired me to pursue research as a future career, which I will proudly continue during my graduate studies. Not only was Dr. Seim an inspiration for my academic endeavors, but also a reliable mentor that loves to listen to my professional and personal aspirations in life as well. 

Equally important to my journey here at UNC is Dr. Ken Zhao, who only recently came to UNC in the summer of 2025, but graciously offered to serve as my second advisor for this project. Dr. Zhao's vast knowledge on ocean modeling was a spark of inspiration for this project, and Dr. Seim and I would not have been able to carry out this project without his support. I am inspired by both Dr. Zhao's youthful motivation and Dr. Seim's wise outlook on oceanographic research, and I hope to represent both my mentors well into the future beyond my time at Carolina. 

I appreciate the support from my fellow labmates (in both the Seim and Zhao labs): Frankie, Jessie, Yubeen, Anya, Tyler, Mason, and Krit. Whether we interacted through group lab meetings, courses, or just talking, I am appreciative of our correspondence and wish everyone the best of luck to their undergraduate/graduate careers at UNC!

I am grateful for the support of the E3P program, the Department of Earth, Marine, and Environmental Sciences, and the department of Mathematics for the invaluable coursework that has prepared me for graduate school. I am also grateful towards the UNC Epsilon Eta Honors Environmental Fraternity, Carolina Science Olympiad, and the many other organizations I have had the pleasure of being involved with at UNC. Their support has made my time here very joyful!

Lastly, I would like to thank my family for their support throughout my life. There are too many of them to thank, but I am especially grateful towards my mother, who never swayed me away from pursuing the sciences as a career. To my sister, Faye, I hope I can be a great inspiration to you as you grow up. 

